%~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~
%	SECTION TITLE
%~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~
\cvsection{Experience}


%~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~
%	CONTENT
%~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~
\begin{cventries}
%---------------------------------------------------------
\cventry
{Project Manager} % Job title
{Founders Approach} % Organization
{Baltimore, MD} % Location
{Dec. 2020 -- Present} % Date(s)
{
      \begin{cvitems} 
        \item {Utilized communication and project management software such as Trello, Slack, Github, and G-suite to lead both native and web application projects.}
        \item {Guided stakeholders through planning, design, devolopment, testing, launch, and maintenance of software applications while utilizing the cost efficiency of international development teams.  }
        \item {Met with both the senior project manager and co-founder regularly to discuss client relations and project status.}
        \item {Maintained, monitored, and in some cases, launched servers and other cloud services for use on projects.}
        \item {Assisted in architrecture and design of technology stacks and cloud infrastructure of projects. }
      \end{cvitems}
    }

%---------------------------------------------------------
\cventry
{Licensed Banker} % Job title
{M\&T Bank} % Organization
{Baltimore, MD} % Location
{Aug. 2017 - Aug. 2020} % Date(s)
{
  \begin{cvitems} % Description(s) of tasks/responsibilities
    \item {Performed routine audits for both federal and internal regulators.}
    \item {Built customer trust through providing solutions to financial needs.}
  \end{cvitems}
}

%---------------------------------------------------------
%---------------------------------------------------------
\cventry
{Assistant Project Manager} % Job title
{Burch Roofing Company} % Organization
{Florence, SC} % Location
{Jun. 2014 - Oct. 2016} % Date(s)
{
  \begin{cvitems} % Description(s) of tasks/responsibilities
    \item {Drafted and presented proposals to potential clients.}
    \item {Acquired needed  permits and licenses for project sites.}
  \end{cvitems}
}

%---------------------------------------------------------
\end{cventries}